\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\setlength{\footskip}{4.1pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
	{\Huge \scshape Alejandro M. Ouslan}
\end{center}

%-----------CONTACT-----------
\begin{center}
	\small (787) 951-6131 $|$
	\href{mailto:alejandro.ouslan@upr.edu}{\underline{alejandro.ouslan@upr.edu}} $|$
	\href{https://linkedin.com/in/ouslan}{\underline{linkedin.com/in/ouslan}} $|$
	\href{https://github.com/ouslan}{\underline{github.com/ouslan}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{M.S. in Statistical Mathematics}{Mayagüez, PR}
{University of Puerto Rico, Mayagüez \quad GPA: 3.36}{Aug. 2024 -- May 2026 (Expected)}

\resumeSubheading
{AEA Summer Program}{Washington, DC}
{Howard University \quad GPA: 3.75}{May 2025 -- Jul. 2025}

\resumeSubheading
{B.A. in Economics}{Mayagüez, PR}
{University of Puerto Rico, Mayagüez \quad GPA: 3.50}{Aug. 2019 -- May 2024}

\resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{Awards \& Publications}
\resumeSubHeadingListStart

\resumeSubheading
{Economic Report for the Governor 2023}{May 2024}
{Puerto Rico Planning Board}{San Juan, PR}
\resumeItemListStart
\resumeItem{Calculated the Human Development Index (HDI) for Puerto Rico (2012–2023) and contributed a chapter to the Economic Report for the Governor 2023.}
\resumeItem{Used data from IPUMS and other government sources.}
\resumeItem{Report available at: \href{https://jp.pr.gov/wp-content/uploads/2024/07/IEG2023-OCE-SA-2024-08598.pdf}{Economic Report PDF}}
\resumeItemListEnd

\resumeSubheading
{Best Graduate Research, Symposium on Applied Economics}{June 2025}
{University of Puerto Rico, Mayagüez}{Mayagüez, PR}
\resumeItemListStart
\resumeItem{Awarded 2nd place for best graduate research.}
\resumeItem{Analyzed the effects of minimum wage changes on employment in foreign versus domestic businesses. Found varying impacts across NAICS sectors, with domestic businesses experiencing a reduction in employment and foreign businesses facing a stronger negative impact.}
\resumeItem{Used uncensored QCEW data from the BLS and applied Bayesian panel regression with fixed effects to estimate the posterior coefficients of the minimum wage on employment.}
\resumeItemListEnd

\resumeSubheading
{Medal of the Department}{May 2024}
{University of Puerto Rico, Mayagüez}{Mayagüez, PR}
\resumeItemListStart
\resumeItem{Recognized for excellence in undergraduate research and maintaining a GPA above 3.5.}
\resumeItemListEnd

\resumeSubheading
{X International Conference in Statistics and Operational Research}{July 2023}
{University of Salamanca}{Salamanca, Spain}
\resumeItemListStart
\resumeItem{Published work on the importance of utilizing advanced tools like Python and SQL in academic research.}
\resumeItem{DOI: \href{https://doi.org/10.14201/0AQ0368}{10.14201/0AQ0368}}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Puerto Rico Planning Board}{Jan. 2024 -- Jul. 2025}
{Lead Developer}{Mayagüez, PR}
\resumeItemListStart
\resumeItem{Led a 15-person team to develop data pipelines for key economic indicators.}
\resumeItem{Utilized Django for the frontend and FastAPI for the backend to build robust and scalable web platforms.}
\resumeItem{Developed API endpoints to download data from government and private sector sources including USA Spending, PR Department of Labor, Census Bureau, PR Planning Board, PR Statistics Institute, Luma Energy, and BLS.}
\resumeItem{Automated data ingestion processes into SQL databases on a monthly, quarterly, and yearly basis.}
\resumeItem{Developed CI/CD pipelines using GitHub Actions, Docker, and Nix to streamline deployment processes.}
\resumeItemListEnd

\resumeSubheading
{Food Security Data Center (SEA), UPRM}{Sept. 2023 -- Jul. 2025}
{Lead Developer}{Mayagüez, PR}
\resumeItemListStart
\resumeItem{Led a team of 5 engineers to develop web platforms for the Experimental Agricultural Station (SEA).}
\resumeItem{Used IPUMS data to calculate caloric intake by county in Puerto Rico and created interactive maps.}
\resumeItem{Developed automation tools for extracting and reporting food establishment data from the QCEW.}
\resumeItemListEnd

\resumeSubheading
{Agricultural Coffee Survey (SEA), UPRM}{Mar. 2024 -- Jul. 2025}
{Lead Developer}{Mayagüez, PR}
\resumeItemListStart
\resumeItem{Led a team of 5 engineers to develop digital survey tools for collecting field data from farmers.}
\resumeItem{Built automation tools to ingest survey data and produce automated reports.}
\resumeItemListEnd

\resumeSubheading
{AEASP, Howard University}{May 2024 -- Jul. 2024}
{AEA Scholar}{Washington, DC}
\resumeItemListStart
\resumeItem{Conducted research with the U.S. Census Bureau on travel time and road infrastructure.}
\resumeItem{Applied spatial regression to assess regional disparities across U.S. PUMAs (2012–2019).}
\resumeItemListEnd

\resumeSubheading
{LEADING Hispanics, USDA}{Sept. 2023 -- Aug. 2024}
{Research Assistant}{Mayagüez, PR}
\resumeItemListStart
\resumeItem{Analyzed the correlation between food deserts and chronic disease prevalence, finding a positive correlation between proximity to food deserts and higher cancer mortality rates.}
\resumeItem{Applied Bayesian Spatial Durbin Model using uncensored QCEW data from the BLS.}
\resumeItem{Evaluated spillover effects using spatial econometrics.}
\resumeItemListEnd

\resumeSubheading
{RUMbo EX, UPRM}{Sept. 2023 -- Jan. 2024}
{Statistics and Economics Tutor}{Mayagüez, PR}
\resumeItemListStart
\resumeItem{Tutored undergraduate students in Microeconomics, Macroeconomics, Econometrics, pre-Calculus I \& II, Calculus I, Statistics I \& II, and Engineering Economic Analysis.}
\resumeItem{Led personalized one-on-one and group sessions with tailored study plans. Prepared simulated exams for students in Calculus.}
\resumeItemListEnd

\resumeSubheading
{L'SPACE HYDROS, NASA}{Jan. 2020 -- May 2020}
{Intern}{Mayagüez, PR}
\resumeItemListStart
\resumeItem{Collaborated with engineers to design a lunar drone for water extraction and prepared a project proposal.}
\resumeItem{Managed the project’s budget, ensuring costs remained below \$10 million.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXTRACURRICULAR-----------
\section{Extracurricular Activities}
\resumeSubHeadingListStart

\resumeSubheading
{University of Salamanca}{Mar. 2023}
{Guest Lecturer}{Salamanca, Spain}
\resumeItemListStart
\resumeItem{Delivered a workshop on Data Science and Research Automation for political science students.}
\resumeItem{Taught web scraping and API integration in Python to create reproducible reports.}
\resumeItemListEnd

\resumeSubheading
{Economics Student Association}{Aug. 2021 -- Jun. 2022}
{Treasurer}{Mayagüez, PR}
\resumeItemListStart
\resumeItem{Managed the association’s budget and tracked expenditures.}
\resumeItem{Organized fundraising events to support student activities and conferences.}
\resumeItemListEnd

\resumeSubheading
{Student Money Association}{Sept. 2019 -- Jun. 2022}
{Student Advisor}{Mayagüez, PR}
\resumeItemListStart
\resumeItem{Assisted students in developing personalized budgets and improving financial literacy.}
\resumeItem{Promoted campus-wide awareness of responsible money management.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills \& Interests}
\begin{itemize}[leftmargin=0.15in, label={}]
	\item \small{
		      \textbf{Skills}: Python, Rust, R, STATA, \LaTeX, SQL, Git, Machine Learning, GIS, GAM, Docker, DevOps, Nix, PyMC
	      }
	\item \small{
		      \textbf{Interests}: Macroeconomics, Spatial Econometrics, Bayesian Inference, Time Series Analysis, Causal Inference
	      }
\end{itemize}

\end{document}
